Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-08-01 literature/paper_draft.qmd
mention h-step CV on NOVELIST

On the other hand, the optimal threshold $\delta^*$ does not have a closed-form solution, and is typically obtained by executing a rolling-window cross-validation procedure. The idea is to find the threshold $\hat{\delta^*}$, with the corresponding $\hat{\lambda}^*$ and $\hat{\boldsymbol{R}}^{N}_{1}(\hat{\delta^*}, \hat{\lambda}^*)$, that minimises the average out-of-sample reconciled forecast errors. The formal algorithm is given in the @sec-novelist_cv Appendix. Although it is not required to fit forecasting models multiple times, the cross-validation procedure is still computationally expensive as it computes the NOVELIST estimator and perform reconciliation for each threshold value.

Note that when $\delta \in \bigl[ \text{max}_{i \neq j}|\hat{r}_{1,ij}|, \; 1 \bigr]$, the NOVELIST estimator collapses to the shrinkage estimator, and when $\delta = 0$, it becomes the sample covariance matrix.

>>>>

On the other hand, the optimal threshold $\delta^*$ does not have a closed-form solution, and is typically obtained by executing a rolling-window cross-validation procedure. The idea is to find the threshold $\hat{\delta^*}$, with the corresponding $\hat{\lambda}^*$ and $\hat{\boldsymbol{R}}^{N}_{1}(\hat{\delta^*}, \hat{\lambda}^*)$, that minimises the average out-of-sample 1-step-ahead reconciled forecast mean squared error over all windows. The formal algorithm is given in the @sec-novelist_cv Appendix. Although it is not required to fit forecasting models multiple times, the cross-validation procedure is still computationally expensive as it computes the NOVELIST estimator and perform reconciliation for each threshold value.

We also tested out minimising 1- to h-step-ahead MSE in the cross-validation procedure. Surprisingly, it returns almost the same best threshold parameter is in the 1-step-ahead case above. Note that when $\delta \in \bigl[ \text{max}_{i \neq j}|\hat{r}_{1,ij}|, \; 1 \bigr]$, the NOVELIST estimator collapses to the shrinkage estimator, and when $\delta = 0$, it becomes the sample covariance matrix.
